---
title: "APIvig"
output: rmarkdown::html_vignette
author: "Group 12"
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{APIvig}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(APIpkg)
```

#Description
Get data from parliament API and return the attendance rate, attitude and participation of each member.

## Shiny application

The shiny application contains **Shiny application** that call and use the data from *APIpkg* package and with use of that data which comes from **vott()** function, draws a histogram. This histogram is frequency of the vote information based on parties.


The histogram can modify with a sidebar with a slider for approve votes.
By slider, user is able to change the number of approve votes pack and get frequency of approve votes inside each pack.


```
shinyApp(ui = ui, server = server)
```


#Usage
```R
APILab
devtools::install_github('AqsaIftikhar25/APILab', build_vignettes = TRUE, force = TRUE)
```
#Import
```R
library(APIpkg)
```

#Examples
l <- vott("C",2015,2020)
runGitHub (repo = "ShinyAPI", username = "AqsaIftikhar25", ref="main")




